This work includes an overview of ion interferometer experiment and a detailed exposition of the construction of the laser system that drives the stimulated Raman transitions.


\chapter{Ion Interferometer Overview}

\section{A Very Basic Overview}
The ion interferometer uses a Mach-Zehnder setup to achieve interferometry with $^{87}$Sr+ ions.
\section{Historical Precedents}
 \subsection{Interferometry}
  The demonstration of interference is crucial to the study of any wave-like phenomenon. 

  A discussion of matter wave interferometry in general. 
  \subsection{Charged Particle Interferometry}
  Electron interferometry using gratings. 

Zero-area-enclosing interferometers used in making clocks. 
\subsection{Cavendish and the history of laboratory-based electromagnetic tests}
  Our experiment's intellectual heritage can be traced directly back to early experiments performed by Cavendish. Cavendish\footnote{the source for this is our lab's oral history--I should source this better} did the initial measurements to verify the $1/r^2$ dependence of Coulomb's law by searching for electric fields \cite{jackson}. 

The best recent
\section{Ion Interferometer Guided Tour}
An ion to be used in the interferometer goes through three distinct stages: trapping and cooling, ionization and, finally, interferometry. 

\subsection{Trapping of Neutral Strontium and LVIS}



\subsection{Ionization of Strontium}

\subsection{Actual Interferometry}

\section{Scope of this work}
My work includes only the construction of the laser that stimulates
